---
title: "Anonymous Work Registration"
author: "CoreyJackson"
date: "11/16/2018"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}

library(ggplot2)
library(plyr)
library(reshape2)
#library(lubridate)
library(data.table)
#library(ggthemes)
library(readr)
#library(ggpubr)
#library(gtools)
#library(wesanderson)
library(knitr)
library(kableExtra)

```

```{r,  include=FALSE, warning=FALSE}
# import datasets 
geordi <- read_csv("~/Dropbox/INSPIRE/Data/System dumps/geordi-1-5-17.csv") # The raw geordi dataet

# remove unnecessary columns 
geordi <- geordi[,-c(3,8,10:17,19)]

#
# First logged in
#

joindate <- ddply(geordi,"userID",summarize,
                  firstclass = min(time))
joindate <- joindate[which(joindate$userID!="(anonymous)"),]

#
# Identifying anonymous events
#

# Find unique IP/user combinations
unique_combination <- unique(geordi[c("userID", "clientIP")])
unique_combination <- unique_combination[which(unique_combination$userID != "(anonymous)"),]

unique_ips <- ddply(unique_combination, c("clientIP"), summarise,
                    userids = length(unique(userID[which(userID != '(anonymous)')]))
                    )

# get IPs only associated with one user account
unique_ips <- unique_ips[which(unique_ips$userids == 1),]
# get their ids 
unique_ips <- merge(unique_ips, unique_combination, by ="clientIP",all.x = TRUE)

# create anon/non anon datasets
geordi_anonymous <- geordi[which(geordi$userID == "(anonymous)"),] # create dataset with only anonymous
geordi_nonanonymous <- geordi[which(geordi$userID != "(anonymous)"),]
remove(geordi)
geordi_anonymous <- merge(geordi_anonymous,unique_ips, by="clientIP", all.x=TRUE) # puts userIDs next to events associated with one userID

# rename/remove columns in both datasets
names(geordi_anonymous)[4]<-"userID" # rename columns
names(geordi_anonymous)[10]<-"userID_a"
geordi_anonymous <- geordi_anonymous[,-c(9)] # remove column
geordi_nonanonymous$userID_a <- geordi_nonanonymous$userID # adds userID to columns to make datasets the same length

geordi <- rbind(geordi_anonymous,geordi_nonanonymous) #Combine anon/non anon events
remove(geordi_anonymous,geordi_nonanonymous,unique_combination) # remove unnecessary dataframes


# concatenate events data
geordi$new.categories <- paste(geordi$type, geordi$relatedID, geordi$data, sep="-")

# get unique events to determine activity
# events <- unique(geordi[c("type","new.categories","breadcrumb")]) completed this step in previous analysis and manually labeled events
events <- read_csv("~/Dropbox/INSPIRE/Papers & Presentations/Anonymous Work (Journal)/events.csv")
# remove highlevel events not needed for analysis
events <- events[which(!is.na(events$new.category)),]
# merge names of events
geordi <- merge(geordi,events, by="new.categories", all.x=TRUE)

# create the original dataset
geordi_org <- geordi

# Combine tutorials events 
geordi$new.category[geordi$new.category %in% c("tutorial - beginner 2","tutorial - beginner 1","tutorial - no training","tutorial - beginner 3","tutorial - apprentice","tutorial - master","tutorial")] <- "tutorial"

# Keep only traces important
geordi <- geordi[which(!geordi$new.category %in% c("close-field-guide","register account","login","register account","click-favorite","link-post","logout","recent-comments-sidebar","view-talk","view-discussion","reply-post","paging")),]
# (talk-view) landing page for list of threads 
# (view-talk) viewing boards from project page. Only boards. Not sure if they clicked
# (view-discussion) viewing a single thread. Not sure where these views origniated. (use talk-N-view as proxy)

# remove events that weren't important
geordi <- geordi[which(!is.na(geordi$new.category)),]
remove(unique_ips,events)
```
## RQ1: Exploring the dataset

Descriptive stats of dataset used in this research  
1. Geordi traces: `r length(geordi$clientIP)`  
2. Users: `r length(joindate$userID)`  
3. IPs `r length(unique(geordi$clientIP))`
4. Trace type after matching:  
    * Logged-In: `r length(geordi$userID[geordi$userID != "(anonymous)"])`   
    * Identified:`r length(geordi$userID[geordi$userID == "(anonymous)" & !is.na(geordi$userID_a)])`  
    * Anonymous: `r length(geordi$userID_a[is.na(geordi$userID_a)])`   

```{r include=FALSE, warning=FALSE}
# get anonymous traces we weren't able to link
geordi_anonymous <- geordi[which(is.na(geordi$userID_a)),]
geordi <- geordi[which(!is.na(geordi$userID_a)),]

## Get events before a user's first loggedin classification
geordi <- merge(geordi,joindate, by.y=("userID"), by.x=("userID_a"), all.x = TRUE)
geordi$preevent <- ifelse(geordi$time < geordi$firstclass,1,0) 

# User future contribution summary
geordi_summary <- ddply(geordi, c("userID_a"), summarize, 
                        activities = length(userID_a),
                        anonymous = length(which(userID=="(anonymous)")),
                        logged_in = length(which(!userID=="(anonymous)")),
                        first_classification = min(firstclass),
                        first_activitiy = min(time),
                        pre_reg_activities = sum(preevent ==1),
                        classifications_future = length(userID_a[new.category=="classify" & preevent == 0]),
                        nonclassification_pre = length(userID_a[new.category != "classify" & preevent == 1])
                        )
geordi_summary$timepre <- geordi_summary$first_classification - geordi_summary$first_activitiy
# number will be diferent from 8606 above because some users don't actually classify. They create accounts and explore the system. 

# Analysis of the geordi_summary. How many users are anonymous/never anonymous etc.
```

```{r, include=FALSE, warning=FALSE}
# The anonymous activities
anonymous_activities <- count(geordi$new.category[which(geordi$userID=="(anonymous)")])
colnames(anonymous_activities)[1] <- "event"

anonymous_activities$event <- factor(anonymous_activities$event, levels=unique(as.character(anonymous_activities$event)) )
anonymous_activities <- transform(anonymous_activities, event=reorder(event, -freq) ) 

allanon <- ggplot(subset(anonymous_activities, event != "classify"), aes(event, freq)) + 
  geom_bar(stat = "identity", fill="dodgerblue4") + 
  coord_flip() + 
  labs(x="Event Category",y="Frequency") + 
  theme(
    axis.text.x=element_text(size=9),
    axis.text.y=element_text(size=9)
  )
```

```{r}
allanon
```

### Other Behaviors

There were `r length(joindate$userID[!(joindate$userID %in% geordi_summary$userID_a)])` users who created accounts, explored the system but never executed a classification.  
```{r include=FALSE, warning=FALSE}
nonclassusers <- joindate$userID[!(joindate$userID %in% geordi_summary$userID_a)]
geordi_regnonclass <-  geordi_org[which(geordi_org$userID %in% nonclassusers),]

```

```{r}

```



## RQ2: Pre-registration anonymous traces
```{r, include=FALSE, warning=FALSE}
# pre-reg and post-reg anon
baregister <- geordi[which(geordi$userID=="(anonymous)"),]
regsummary <- ddply(baregister, c("new.category","preevent"), summarise,
                    count = length(new.category)
)

regsummary$preevent <- factor(regsummary$preevent)
regsummary <- na.omit(regsummary)

regsummary$new.category <- factor(regsummary$new.category, levels=unique(as.character(regsummary$new.category)) )
regsummary <- transform(regsummary, new.category=reorder(new.category, -count) ) 

anon_prepost <- ggplot(subset(regsummary, new.category != "classify"), aes(new.category,count, fill=preevent)) + 
  geom_bar(stat = "identity") + scale_fill_manual(labels = c("Pre-reg.", "Post-reg."),values = c("deepskyblue4","orangered1")) + coord_flip() +
  labs(x="Activities",y="Number of Activities") +
  guides(fill=guide_legend(title="Type")) + 
  scale_x_discrete(NULL, expand = waiver(), position = "bottom") 

## Categories of activity
prereg_summary <- ddply(prereg, c("new.category"), summarize,
                         users = length(unique(userID_a)),
                         count = length(userID_a)
                         )
# Pre-reg
prereg_summary$event <- factor(prereg_summary$new.category, levels=unique(as.character(prereg_summary$new.category)) )
prereg_summary <- transform(prereg_summary, new.category=reorder(new.category, -count) ) 

# Pre-registration activities
anon_prereg <- ggplot(subset(prereg_summary, new.category != "classify"), aes(new.category, count)) +
  geom_bar(stat = "identity", fill="dodgerblue4") + 
  coord_flip() + 
  labs(x="Event Category",y="Frequency") + 
  theme(
    axis.text.x=element_text(size=9),
    axis.text.y=element_text(size=9)
  )

## Individual users 
geordi_summarypre <- geordi_summary[which(geordi_summary$pre_reg_activities !=0),]

geordi_summarypre$f <- as.Date(as.character(geordi_summarypre$first_classification), format="%Y-%m-%d")
geordi_summarypre$a <- as.Date(as.character(geordi_summarypre$first_activitiy), format="%Y-%m-%d")

geordi_summarypre$diff_in_days <- as.numeric(difftime(geordi_summarypre$f ,geordi_summarypre$a , units = c("days")))
geordi_summarypre$f <- NULL
geordi_summarypre$a <- NULL

```

Here we review the pre-registration traces of volunteers who we were able to link anonymous traces to their user accounts.
```{r}
anon_prereg

kable(prereg_summary, "html", 
      caption = "Gravity Spy Pre-registration activities", booktabs = T) %>%
kable_styling()

```

## RQ3: Post-registration anonymous traces
```{r, include=FALSE, warning=FALSE}


```

Here we review the post-registration traces of volunteers who we were able to link anonymous traces to their user accounts.
```{r}

```

```{r}
anon_prepost
```


## RQ4: Participation intention
```{r, include=FALSE, warning=FALSE}


```

```{r}

```

## RQ5. Participation around signing in for known volunteers

